Monte Carlo and bootstrap for ALL parameters

### 2024-08-09 All_param.Rmd
est_boot not good yet

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

>>>>

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  big_est <- as.data.frame(matrix(NA, ncol = nb_var, nrow = nboot))

  # Estimations of totals
  for (c in 1:nboot) {
    big_est <- mapply(function(vec_, j){
        vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
        return(as.data.frame(vec_))
        }, big_est, 1:nb_var)
    # (n/(n-1)) is the correction needed since we choose only (n-1) points

        # big_est2 <- mapply(function(vec_, j){
        # vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
        # return(as.data.frame(vec_))
        # }, big_est2, 1:nb_var) 
    # mapply(function(vec_, c){append(vec_, (n/(n-1))*sum(df[, 2 + c + ((nb_var+2)*(c-1))]/p))}, big_vec, 1:nboot)
    # vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
    # vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
    # vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
  }
  # Estimations of ratios
  l_big_est <- length(big_est)
  big_est <- as.data.frame(big_est)
  for (k in 1:4) {
    big_est <- add_column(big_est, rep(NA, nrow(big_est)))
  }
  big_est2 <- big_est
  for (c in 1:nboot) {
    # add_column()
    big_est2 <- mapply(function(j){big_est2[c, l_big_est+j] <- big_est2[c,j+4]/big_est2[c,j]
      return(as.data.frame(big_est2))
    }, 1) # 4 ratios
    # big_est2[l_big_est+1] <- big_est2[c,1]/big_est2[c,1+4]

    test <- function(j){big_est2[c, l_big_est+j] <- big_est2[c,j+4]/big_est2[c,j]     
    return(as.data.frame(big_est2))
    }
  }
  big_est <- t(big_est)
  colnames(big_est) <- c("est_nb", "est_nb_s","est_nb_m", "est_nb_b", "est_vol", "est_vol_s", "est_vol_m", "est_vol_b")
  # vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(big_est)
  # Data frame with 3 estimations for each sample
}
```
